Flexible Scientific Data Management for Plant Phenomics Research

### 2013-04-15 s4biodiv2013/Rebuttals.txt

 *****

Overall, I thought the manuscript was unnecessarily opaque, didn't emphasise the primary themes of "biodiversity" and "semantics", and over-emphasised many other aspects of their phenotype acquisition and processing workflow.  It's not a bad manuscript, at all, and is likely very well-suited for submission elsewhere (if made slighly less "jargony")!  However, I don't see the fit with this meeting, unless it is extensively re-written.

 *****

 Rebuttal : We feel that the reviewer did not recognise the attempt to provide a high level view of the integrated PODD and PlantScan system and how it is being used by HRPPC to process plant phenomics data (Section 2). Plant phenomics is a legitimate subset of biodiversity. It highlights differences between, and inside, multiple plant species based on feature comparisons. This paper provides a description of the high level use of ontologies to structure and enrich a semantic data model based on RDF and OWL. OWL is used in PODD for both syntactic validation and sparse semantic enrichment purposes.

 The reviewer requests that the manuscript use less jargon, but also detail more specifically what ontologies are in use and how they are being practically used, which entails using more jargon related to those specific ontologies.

### 2013-04-15 s4biodiv2013/PODD-S4BIODIV-Submission.tex
update figure

\section{Introduction}
Since the genomics era, biology has become a data-driven science. Advances in
robotics, automation and imaging, in combination with high performance computing
have permitted the rapid production of large and complex biological datasets.
Currently, high volumes of heterogeneous image data, physiological and
morphological measurements are being acquired by a range of new phenotyping
platforms located in purpose built phenomics centres across the world. These
large datasets of phenotypic characteristics such as growth rate, plant architecture,
photosynthetic performance, yield must be stored and correlated with genotypes. These factors provide evidence of genetic variation in natural and derived genetic populations (e.g. germplasm collections, association genetic panels, recombinant inbred lines). They also enable a deeper understanding the dynamic relationship between phenotype, genotype and environment which is necessary to continue delivering the increase in productivity necessary for feeding the world.

@@

OWL is used to determine whether projects are both internally consistent, with
all objects having an explicit RDF type, and whether they are consistent with
the ontologies that they import. 
%The main point that PODD focuses on for
%validation is determining that mappings are consistent with the basic PODD
%predicates and classes, so that they can be used to render both static HTML
%pages and provide HTML based editing facilities. 
For example, any OWL object
property that has been defined to link from image acquisition runs to images can
be used to define the purpose of an image. This may include any combination of
the defined properties, without requiring all of the properties to be used.
% The parent object types and properties used by PODD to establish basic ground
% rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are defined
in optional extension ontologies as illustrated in Figure~\ref{poddontologies}.
These are used by scientists to annotate their projects with concepts specific 
to their field, without requiring other scientists using the system to use phenotype 
properties to annotate their projects.

>>>>

\section{Introduction}
Since the genomics era, biology has become a data-driven science. Advances in
robotics, automation and imaging, in combination with high performance computing
have permitted the rapid production of large and complex biological datasets.
Currently, high volumes of heterogeneous image data, physiological and
morphological measurements are being acquired by a range of new phenotyping
platforms located in purpose built phenomics centres across the world. These
large datasets of phenotypic characteristics such as growth rate, plant architecture,
photosynthetic performance, yield must be stored and correlated with genotypes. 
These factors provide evidence of genetic variation in natural and derived genetic 
populations (e.g. germplasm collections, association genetic panels, recombinant inbred 
lines). They also enable a deeper understanding of the dynamic relationship between 
phenotype, genotype and environment which is necessary to continue delivering the 
increase in productivity necessary for feeding the world.

@@

OWL is used to determine whether projects are both internally consistent, with
all objects having an explicit RDF type, and whether they are consistent with
the ontologies that they import. 
%The main point that PODD focuses on for
%validation is determining that mappings are consistent with the basic PODD
%predicates and classes, so that they can be used to render both static HTML
%pages and provide HTML based editing facilities. 
For example, any OWL object
property that has been defined to link from image acquisition runs to images can
be used to define the purpose of an image. This may include any combination of
the defined properties, without requiring all of the properties to be used.
% The parent object types and properties used by PODD to establish basic ground
% rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are defined
in optional extension ontologies as illustrated in Figure~\ref{poddontologies}.
These are used by scientists to annotate their projects with concepts specific 
to their field, without requiring other scientists using the same PODD installation 
to use phenotype properties to annotate their projects.
